Manuscript for foodborne-outbreak Project

### 2023-02-24 products/manuscript/Manuscript.qmd
part 2 work

set up
```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(broom)
library(ggtext)
```

@@

As previously mentioned, the data was acquired from [Kaggle](https://www.kaggle.com/datasets/cdc/foodborne-diseases) and [CDC] (https://wwwn.cdc.gov/norsdashboard/).

@@

## Statistical Analysis
Post-preprocessing, we performed an exploratory data analysis to view general relationships between the predictors: time (year), pathogen type and etiology, state, food type, and health outcomes of interest: hospitalizations and illnesses.

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(broom)
library(ggtext)
```

@@

As previously mentioned, the data was acquired from [Kaggle](https://www.kaggle.com/datasets/cdc/foodborne-diseases) and the [CDC](https://wwwn.cdc.gov/norsdashboard/) [@cdc2017; @cdc2020a].

@@

## Statistical Analysis

Post-preprocessing, we performed an exploratory data analysis to view general relationships between the predictors: time (year), pathogen type and etiology, state, food type, and health outcomes of interest: hospitalizations and illnesses.
